---
title: "Formatted list of authors"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: word_document
params:
  input: "authors_affiliations.tsv"
---

<!-- Convert sorted tsv file with author names and affiliations -->
<!-- to author list in word document for usage in a manuscript -->

<!-- Assumptions: -->
<!-- - input file contains columns 'Author name' and 'affiliation 1', 'affiliation 2', ... -->
<!-- - rows are sorted by desired occurence of authors on manuscript -->


## Assumptions

- required columns:
  - `Author name`
  - `affiliation 1`, `affiliation 2`, ...
- rows in input tsv are sorted by desired order of authors on manuscript
- in output, affiliation indices per author are sorted numerically


## Processing steps

- remove all superfluous whitespaces in author names and affiliations
- exclude affiliation "C" (-> error in input?)
- format any listed name initials as X.
- consistently use USA (not US) as country code in affiliations
- consistently use UK (not GB) as country code in affiliations



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(here)
library(data.table)

dat <- fread(params$input, encoding = 'UTF-8') %>% as_tibble() %>%
  set_names(make.names(colnames(.))) %>%
  select(author = Author.name, contains("affiliation.")) %>%
  mutate_all(~ str_squish(.x)) %>%
  mutate(author = str_replace_all(author, "\\b([[:alpha:]])\\b(?!\\.)", "\\1\\.")) %>%
  mutate(author_rank = 1:nrow(.)) %>%
  pivot_longer(cols = contains("affiliation."), 
               names_to = "affil_rank_author",
               values_to = "affil") %>%
  mutate(affil_rank_author = as.integer(str_extract(affil_rank_author, "\\d+"))) %>%
  filter(affil != "") %>%
  filter(affil != "C") %>% 
  mutate(affil = str_replace(affil, "\\bUSA?$", "USA"),
         affil = str_replace(affil, "\\bGB$", "UK")) %>% 
  mutate(affil_rank = as.numeric(factor(affil, levels = unique(affil))))
```

## List of similar affiliations (to look for errors)

```{r}
# unique affiliations in data
uaffil <- unique(dat$affil)

# fuzzy matching to other listed affiliations (only return imperfect matches)
affilmatch <- lapply(seq_along(uaffil), function(i) {
  agrep(uaffil[i], uaffil[-(1:i)], ignore.case = T, value = T)
}) %>% 
  set_names(uaffil) %>% 
  .[sapply(., function(x) length(x) > 0)]
```

`r sapply(seq_along(affilmatch), function(i) {
  paste0("- ", names(affilmatch)[i], "\n",
         paste0("  - ", affilmatch[[i]], "\n", collapse = ""))
}) %>% paste0(collapse = "")`


## Authors

```{r authors}
# compose formatted string of authors
authors <- dat %>%
  group_by(author_rank, author) %>%
  arrange(affil_rank) %>% 
  summarize(aff_ranks = paste0(affil_rank, collapse = ","),
            string = paste0(unique(author), "^", aff_ranks, "^")) %>% 
  ungroup() %>%
  summarize(out = paste0(string, collapse = ", ")) %>% .$out
```

`r authors`  


## Affiliations

```{r affiliations}
# compose formatted string of affiliations
affiliations <- dat %>% 
  select(affil, affil_rank) %>% 
  filter(!duplicated(affil)) %>% 
  summarize(out = paste0("^", affil_rank, "^", affil, ".", 
                         collapse = " ")) %>% 
  .$out
```


`r affiliations`
